Clustering galaxies at 0.5 < $z$ < 1: data mining approach

### 2016-03-31 main.tex
End of Draft 0.0

\begin{abstract} 
In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.
In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.
We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.

@@

\import{sections/}{intro0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\import{sections/}{data0.0.tex}

@@

\import{sections/}{method0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{sections/}{results0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Discussion
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

%\import{sections/}{diss0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{SUMMARY}
\label{sec: summary}
1) we used SOM blah blah balh.
\newline
2) with this method we not only can categorized the galaxies with more precision but also we could recognize the galaxies have similarity to two or more groups of galaxies.
\newline
3) This method can help us to find outliers or new categories of galaxies very easily  and fast.

\section*{ACKNOWLEDGMENTS}
S.R. and P.B. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mnras}
\bibliography{ref_mining_h.bib}

\import{sections/}{apps0.0.tex}
\end{document}

>>>>

\begin{abstract} %Most of this abstract is just a filler
In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
We obtain physical properties of the sample galaxies measured using {\em CIGALE} code to study and compare the properties of each cluster.
In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
%%%%%%From this point it is just repeated%%%%%%%%%
We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.
We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.

@@

\import{sections0.0/}{intro0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\import{sections0.0/}{data0.0.tex}

@@

\import{sections0.0/}{method0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{sections0.0/}{results0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Discussion
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

%\import{sections0.0/}{diss0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{SUMMARY}
\label{sec: summary}
1) We introduced the self organizing maps to be used to categorizing the SED of galaxies.
\newline
2) Using this method we not only can categorized the galaxies with more precision but also we could recognize the galaxies have similarity to two or more groups of galaxies.
\newline
3) This method can help us to find outliers or new categories of galaxies very easily  and fast.

4) ...
\section*{ACKNOWLEDGMENTS}
S.R. and P.B. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mnras}
\bibliography{ref_mining_h.bib}

\import{sections0.0/}{apps0.0.tex}
\end{document}

### 2016-03-31 sections0.0/data0.0.tex
End of Draft 0.0

 \subsection{SED and Properties of the sample galaxies}
    T12 selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field, which have a photometry data from the Good-MUSIC catalogue. 
    The photometry data contains data in 10 - 13 filters with wavelength range of $\sim 0.4-24 \mu$m. 
    They used these photometry data as inputs for Code Investigating GALaxy Emission (CIGALE code;~\citep{Noll09}) to generate the best fitted SED for each galaxy as well as some of the physical properties of the galaxies.

    CIGALE is a valuable tool to investigate the properties of the galaxy using UV to IR wavebands.
    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei's optical spectral templates to model SED of the galaxies.
    This code were successfully tested with data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by N09.
    T12 produced the best SED match for each galaxies.
    For testing the created networks, we only used part of the spectra that have the same wavelength as K96 SEDs.
    Then, they used an exponentially decreasing SFR, visual attenuation ($\tau$) model and derived physical properties of galaxies such as age, and stellar mass.
    They assumed the Salpeter initial mass function~\citep{Salpeter55} and old stellar population age of $\sim 10$~Gyr.More details on creating SEDs and extracting information about galaxies properties using CIGALE can be found in N09 and T12.

>>>>

 \subsection{SED and Properties of the sample galaxies}
    T12 selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field, which have a photometry data from the Good-MUSIC catalogue. 
    The photometry data contains data in 10 - 13 filters with wavelength range of $\sim 0.4-24 \mu$m. 
    They used these photometry data as inputs for Code Investigating GALaxy Emission ({\em CIGALE} code;~\citep{Noll09}) to generate the best fitted SED for each galaxy as well as some of the physical properties of the galaxies.

    {\em CIGALE} is a valuable tool to investigate the properties of the galaxy using UV to IR wavebands.
    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei's optical spectral templates to model SED of the galaxies.
    This code were successfully tested with data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by N09.
    T12 produced the best SED match for each galaxies.
    For testing the created networks, we only used part of the spectra that have the same wavelength as K96 SEDs.
    Then, they used an exponentially decreasing SFR, visual attenuation ($\tau$) model and derived physical properties of galaxies such as age, and stellar mass.
    Some of these properties are shown in Tab~\ref{tab: props}.
    In the Sec.~\ref{sec: 1D}, we studied these properties for each categorization.
    They assumed the Salpeter initial mass function~\citep{Salpeter55} and old stellar population age of $\sim 10$~Gyr.
    More details on creating SEDs and extracting information about galaxies properties using {\em CIGALE} can be found in N09 and T12.

    \begin{table}
\caption[]{Description of the properties of T12 galaxies; the output result of {\em CIGALE}}     
\label{tab: props}
\centering
\begin{tabular}{l l l}
\hline\hline
\noalign{\smallskip}
Par. & Unit & Description\\
\noalign{\smallskip}
\hline
\noalign{\smallskip}
$t_{\,\mathrm{oSP}}$ & Gyr & age of old SP model \\
$t_{\,\mathrm{ySP}}$ & Gyr & age of young SP model \\
$f_\mathrm{burst}$ & --- & mass fraction of \\
& & young SP model \\
\noalign{\smallskip}
$t_{\,\mathrm{D4000}}$ & Gyr & D4000-related age. \\
\noalign{\smallskip}
$M_\mathrm{star}$ & M$_\odot$ & total stellar mass  \\
SFR & M$_\odot$/yr & instantaneous SFR  \\
\noalign{\smallskip}
\hline
\end{tabular}
\end{table}

### 2016-03-31 sections0.0/method0.0.tex
End of Draft 0.0

 \cite{Geach12} presented the application of the SOM and demonstrate the algorithm of the SOM in detail. In this section we are going to talk briefly about the algorithm of the SOM, how we create our maps and a test model which will help to interpret our results. %PB20160218: contrast SOM with principal component analysis (PCA), which may be more familiar?

 \subsubsection{Algorithm of SOM} 
 \label{sec: algorithm}
     Assuming we have a data set which contains vectors, \boldit{V} $\in \Re^n$ and we want to map them on S1 by S2 map. 
     We start by creating S1 $\times$ S2 empty neurons. 
     The initial arrangement of these neurons depends on a map's topology provided by user.
     Since the topology of the map does not have any affect on the final result, we chose hexagonal topology which is the default topology for SOMs.
     Then, we assign a random weight vector \boldit{W} $\in \Re^n$ to each node.
     The process of creating SOM, happens over series of $N$ iterations. 
     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
      In each iteration:
     \begin{enumerate}
        \item Choose a random vector from our data set.
        \item Calculate the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and find a neuron with ``$D_{j_{min}}$". This neuron is the winner node and is calling Best Matching Unit (BMU). 
        \item  Compute the radius of the neighbourhood of the BMU to find nodes within this radius. The weight vectors of these nodes will be affected in the next steps. This value is arbitrary and initially can be set to be as high as half of the SOM size and then it decades exponentially over each iteration:
        \begin{equation}
            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
        \end{equation}
        where $\tau$ is a decay constant and usually set to be the same as number of iterations, $N$. $r^0_{BMU}$ and $r^t_{BMU}$ is the radius of the neighbourhood at 0th and $t$th iteration, respectively. 
        \item Change the weight vectors of the BMU and all the nodes within r(t) as:
        \begin{equation}
            \label{equ: weight adj}
            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
        \end{equation}
        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate. $R(t)$ determines how weight of nodes in the neighbourhood of BMU will change.
        \item  Repeat these steps for $N$ times.
     \end{enumerate}

\subsection{Creating SOM}
\label{sec: create_som}
     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
     SOM in {\tiny NNT} can be created by {\tiny newsom} library which works in two phases. 
     Phase one is the ``ordering phase". 
     This phase starts with maximum neighbourhood distance, and initial high learning factor usually 0.9 which is provided by user. 
     The ordering phase continues for requested number of iterations and it continues till the learning factor reduces to tuning phase leaning factor and the neighbourhood distance reaches to the number set by the user.

@@

    %Although size of the SOM could be anything \cite{Vesanto05} suggested that the total number of  $5\sqrt{n}$ neurons provides the most sufficient size.
     Size of SOM maps is arbitrary and there is no rules or restrictions on choosing the size of maps. 
     Users usually must choose the size of grids based on their data set and their usages of the results.
     For our 10 regions we created maps with sizes from $1\times2$ to $50\times50$ to choose the sufficient size for our maps.
     varying grids of the maps helps us to monitor whether grouping regions in smaller maps is real or its because of the shortage of the neurons.
     Based on size of our data and our results, we chose max of the grid size to be 1$\times$10 and 10$\times$10 in 1D and 2D maps, respectively.

>>>>

 \cite{Geach12} presented the application of the SOM and demonstrate the algorithm of the SOM in detail. In this section we are going to talk briefly about the algorithm of the SOM, how we create our maps and a test model which will help to interpret our results. 
 \subsubsection{Algorithm of SOM} 
 \label{sec: algorithm}
     Assuming we have a data set which contains vectors, \boldit{V} $\in \Re^n$ and we want to map them on S1 by S2 map. 
     We start by creating S1 $\times$ S2 empty neurons. 
     The initial arrangement of these neurons depends on a map's topology provided by user.
     Since the topology of the map does not have any affect on the final result, we chose hexagonal topology which is the default topology for SOMs.
     Then, we assign a random weight vector \boldit{W} $\in \Re^n$ to each node.
     The process of creating SOM, happens over series of $N$ iterations. 
     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
      In each iteration:
     \begin{enumerate}
        \item Choose a random vector from our data set.
        \item Calculate the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and find a neuron with ``$D_{j_{min}}$". This neuron is the winner node and is calling Best Matching Unit (BMU). 
        \item  Compute the radius of the neighbourhood of the BMU to find nodes within this radius. The weight vectors of these nodes will be affected in the next steps. This value is arbitrary and initially can be set to be as high as half of the SOM size and then it decades exponentially over each iteration:
        \begin{equation}
            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
        \end{equation}
        where $\tau$ is a decay constant and usually set to be the same as number of iterations, $N$. $r^0_{BMU}$ and $r^t_{BMU}$ is the radius of the neighbourhood at 0th and $t$th iteration, respectively. 
        \item Change the weight vectors of the BMU and all the nodes within r(t) as:
        \begin{equation}
            \label{equ: weight adj}
            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
        \end{equation}
        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate. $R(t)$ determines how weight of nodes in the neighbourhood of BMU will change.
        \item  Repeat these steps for $N$ times.
     \end{enumerate}

\subsection{Creating SOM}
\label{sec: create_som}
     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
     SOM in {\tiny NNT} can be created by {\tiny newsom} or {\tiny selforgmap} library which both work in two phases. 
     Phase one is the ``ordering phase". 
     This phase starts with maximum neighbourhood distance, and initial high learning factor usually 0.9 which is provided by user. 
     The ordering phase continues for requested number of iterations and it continues till the learning factor reduces to tuning phase leaning factor and the neighbourhood distance reaches to the number set by the user.

@@

    %Although size of the SOM could be anything \cite{Vesanto05} suggested that the total number of  $5\sqrt{n}$ neurons provides the most sufficient size.
     Size of SOM maps is arbitrary and there is no rules or restrictions on choosing the size of maps. 
     Users usually must choose the size of grids based on their data set and their usages of the results.
     For training networks using 12 galaxies from K96, we created maps with sizes from $1\times2$ to $50\times50$ to choose the sufficient size.
     varying grids of the maps helps us to monitor whether grouping galaxies in smaller maps is because they have similar SEDs or its because of the shortage of the neurons.
     Based on size of our data and our results, we chose max of the grid size to be 1$\times$22 and 12$\times$12 in 1D and 2D maps, respectively.

### 2016-03-31 sections0.0/results0.0.tex
End of Draft 0.0

        \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
            We used each network that we trained in Sec.~\ref{sec: 1Dt}, to classifying the sample 142 galaxies from T12.
            Upper plot in the Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1 \times 2$~network from Fig.~\ref{fig: 1by2T}.
            It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to star burst galaxies.
            The lower plot shows the average SED of the SEDs galaxies in each node. 
            The left plot shows the average SED of 80 galaxies that classify as an early type galaxies. 
            These are the similar ones sit on the left node in the upper plot in the Fig.~\ref{fig: 1by2T}.
            The plots clearly shows the 4000\AA~break in the SEDs, which is the one of the signatures of the SED of the early type galaxies.
            The strong the emission line in that figure comes from the galaxies with similar SED to Sa galaxies but with more strong emission lines.
            The right plot in the lower part of the Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are the signs of the strong star formation in the galaxies. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.55\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies from K96. Up: Numbers in each node represents the number of galaxies that belong to that group. In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the star burst galaxies. Down: Average SED of the SEDs of the galaxies in each group. the left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (star burst ones).}
                \label{fig: 1by2V}
            \end{figure}            
            Since in this network galaxies forced to divided to two groups, for any SED between these two groups the SOM decides that the galaxy belongs to which group based on the strongest features of its SED.
            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as star bursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
            Increasing the size of the SOM helps to solve problem of the galaxies which have features of both groups.

@@

        \subsubsection{1D NETWORKS results and Properties of galaxies}

    \subsection{2D SOMs}
    \label{sec: 2D}
    Although the 1D networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies in each category, each neurons in these networks is limited to be connected to on other neurons in each direction.
    Since each neuron can have more than two immediate neighbours in the 2D networks, they provide more complete pictures of the relation between each SED type.
    For analysing 2D networks, we consider two approaches; at first we assumed that all the galac

    \subsection{Caveat}
    There is no established method to find the best SOM initial values. Size of the maps, number of neighbours in each steps, number of iterations could vary and each one give us a new result.
    Also, since at the beginning the weights are generated randomly, in each run the results could have small differences.

>>>>

        \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
         \label{sec: 1Dv}
            We used each network that we trained in Sec.~\ref{sec: 1Dt}, to classifying the sample 142 galaxies from T12.
            Upper plot in the Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1 \times 2$~network from Fig.~\ref{fig: 1by2T}.
            It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to star burst galaxies.
            The lower plot shows the average SED of the SEDs galaxies in each node. 
            The left plot shows the average SED of 80 galaxies that classify as an early type galaxies. 
            These are the similar ones sit on the left node in the upper plot in the Fig.~\ref{fig: 1by2T}.
            The plots clearly shows the 4000\AA~break in the SEDs, which is the one of the signatures of the SED of the early type galaxies.
            The strong the emission line in that figure comes from the galaxies with similar SED to Sa galaxies but with more strong emission lines.
            The right plot in the lower part of the Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are the signs of the strong star formation in the galaxies. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.55\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies from K96. Up: Numbers in each node represents the number of galaxies that belong to that group. In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the star burst galaxies. Down: Average SED of the SEDs of the galaxies in each group. the left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (star burst ones).}
                \label{fig: 1by2V}
            \end{figure}            
            Since in this network galaxies forced to divided to two groups, for any SED between these two groups the SOM decides that the galaxy belongs to which group based on the strongest features of its SED.
            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as star bursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
            Increasing the size of the SOM helps to solve problem of the galaxies which have features of both groups.

@@

        \subsubsection{1D NETWORKS results and Properties of galaxies}
        In order to check weather our conclusions in Sec.~\ref{sec: 1Dv}~is meaningful and correct, we plot the some physical properties listed in the Tab.~\ref{tab: props} of galaxies in each neurons in the networks.

        \begin{figure}
            \centering
            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_2.png}
            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by2V}}
            \label{fig: prop1by2}
        \end{figure}

                \begin{figure}
            \centering
            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_3.png}
            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by3V}}
            \label{fig: prop1by3}
        \end{figure}

                \begin{figure}
            \centering
            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_22.png}
            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by22V}}
            \label{fig: prop1by22}
        \end{figure}

        Figs.~\ref{fig: prop1by2} to ~\ref{fig: prop1by22} show the results of median of stellar mass, age, specific star formation rate (SSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each nodes in the upper maps of the Figs.~\ref{fig: 1by2V} to ~\ref{fig: 1by22V}.
        In all the plots $x$-axis shows the number of the neurons from left to right, and $y$-axis shows one of the mentioned properties.

        In Fig.~\ref{fig: prop1by2}, from early type galaxies to star burst ones, stellar mass and age decreases while SSFR and $f_\mathrm{burst}$ increases. 
        The same trend is noticeable in both Fig.~\ref{fig: prop1by3} and Fig.~\ref{fig: prop1by22}. 
        The gaps in the Fig.~\ref{fig: prop1by22} is due to the empty neurons in Fig.~\ref{fig: 1by22V}. These trends are another evidence that this method is working properly and can be used to categorized galaxies based on their SEDs or even their physical properties.

    \subsection{2D SOMs}
    \label{sec: 2D}
    Although the 1D networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies in each category, each neurons in these networks is limited to be connected to on other neurons in each direction.
    Since each neuron can have more than two immediate neighbours in the 2D networks, they provide more complete pictures of the relation between each SED type.
    As described in the Sec.\ref{sec: method}, one of the main advantages of the SOM method is when weight of one neurons is adjusted after finding the BMU, weight of the whole map will be changed.
    This quality of the SOMs provide us an opportunity to analysing 2D networks in two approaches. 
    At first, as we had in the 1D SOMs, we assumed that all the galaxies must have SEDs similar to any of the 12 models in Fig.~\ref{fig: k96}.
    For the second path, we trained networks assuming that there might be some other and completely different types of the galaxies that we never encountered with before.
    Second approach could be used to trace the outliers as well.

    %maybe I should move the following paragraph to method section?! I am not sure, yet.
    For getting the best result from both of these ways, we should have SOMs with high ``enough"  neurons to give any new sets of galaxies a chance to find their best place in the map.
    The  high ``enough"  neurons is a vague statement, but as mentioned in the Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and what kind of the information you need from the SOMs.
    Since the training data (K96 ones) have 12 galaxies, we assumed a SOM with size of $8\times8$~would be a good start.
    We then increased the size of SOM to find the highest size suitable for the training sample.
    We noticed that SOMs with size of $12\times12$~are the maximum possible choice.
    With increasing from $12\times12$~neurons, the SOMs would be repeat the same shapes just in bigger grids.

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/2d/dist_12_by_12.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../images/2d/hit_t_12_by_12.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
        \end{subfigure}
        \caption{Results of training network in $12\times12$~grid, when we considered that there are only 12 types of SEDs for galaxies.}
        \label{fig: 12by12T_newsom}
    \end{figure}
    Fig.~\ref{fig: 12by12T_newsom} shows the SOM results for the first approach. 
    Since we considered that SEDs of all galaxies can be categorized using the K96 model, the galaxies took place all over the map.
    Using this network to categorize any set of SEDs, forced the SEDs to be in the same neurons as the K96 ones or the neurons between them.
    However, all the K96 galaxies are in small side of the map in Fig.~\ref{fig: 12by12T_selforg}, which provide enough freedom for SED of the galaxies to take place everywhere in the map even it is way far away from the K96 samples.
    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/2d/dist_12_by_self_org_res12.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../images/2d/hit_t_12_by_self_org_res12.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
        \end{subfigure}
        \caption{Results of training network in $12\times12$~grid, when we considered that there might be some outlier or other type of SEDs.}
        \label{fig: 12by12T_selforg}
    \end{figure}

    In the upper map in Fig.~\ref{fig: 12by12T_newsom}, there is a strip of the red, dark red and in some case black colours is distinguishable. 
    This strip is separating early type galaxies with star burst ones.
    The lower map shows that 5 of the neurons on left side of the strip are full. 
    These 5s are the same ones in the left hand side of the Fig.~\ref{fig: 1by2T} (early type galaxies).
    The only difference is that here, in this map they have more space to be separated from each other.
    When we use this network to categorized the SED of galaxies any galaxy places on the left hand side of the strip is an early type galaxy and any one placed in the right side of the strip is a star burst one.
    Decision about what type of the early type or star burst galaxy is it, is based upon its relative position to each type in the neurons.

    The border between the early type galaxies and the star burst ones,in the Fig.~\ref{fig: 12by12T_selforg}, is the black strips in the middle of the upper map, which end up with bright red colour at the bottom of the map in the fifth neuron.
    In this network, neurons in the right side of the strip represent the early type galaxies and the neurons in the left side represent the star burst ones.
    In case of the categorizing a new set of SEDs, if the new SEDs are similar to K96 sample all of them will place in the bottom of the map, but if there are different type of the galaxies, they would sit in any other neurons in the map.

    We used the both 2D networks to categorized the T12 galaxies and showed the results in Fig.~\ref{fig: 12by12V}.
    In the lower plot, we used the network from Fig.~\ref{fig: 12by12T_selforg}.
    Since all the galaxies placed in the bottom part of the map, we can conclude that there in no outlier or very different type of the SED in from K96 models in T12 samples.
    The upper plot of the Fig.~\ref{fig: 12by12V} represents the T12 galaxies categorization based on the network in the Fig.~\ref{fig: 12by12T_newsom}. 
    In both maps in the Fig.~\ref{fig: 12by12V}, majority of the galaxies are in the early type side of the SOM, which was predictable from the results in the Sec.\ref{sec: 1Dv}.

       \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/2d/hit_v_12_by_12.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../images/2d/hit_v_12_by_self_org_res12.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
        \end{subfigure}
        \caption{Results of categorizing T12 galaxies using $12\times12$~network. Up: categorizing with network shown in Fig.~\ref{fig: 12by12T_newsom}. Down: using network in Fig.~\ref{fig: 12by12T_selforg}.}
        \label{fig: 12by12V}
    \end{figure}

    Although because of the fluency of the paper, we first talked about 1D networks and continued to 2D networks we suggest that in case of using the SOMs to categorize the SED of the galaxies or to explore any related data, first step to be checking data using networks similar to the Fig.~\ref{fig: 12by12T_selforg} ones.
    In this case, all the outlier or specific cases would be identified and removed from the sample.

    \subsection{Caveat}
    There is no established method to find the best SOM initial values. Size of the maps, number of neighbours in each steps, number of iterations could vary and each one give us a new result.
    Also, since at the beginning the weights are generated randomly, in each run the results could have small differences.
    %no quantitative way to analyse the data?!
